SPARQL on the open, decentralised Web

### 2016-06-02 dissertation/motivation.tex
philosophy of science

>>>>

\subsection{Philosophy of Science}

While a failure to be developer friendly may be one reason why the
Semantic Web has not succeeded at a grand scale, my training in
natural science lead me to ask if there may be other reasons that we
do not see the remarkable rate of progress of the natural sciences in
this field. These questions are as hard to ask and to live with as to
answer.
